\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
get rid of comments.
move flow figures next to each other; resize flow and redesign figures.
Merge both flow diagrams into one figure and write a caption.

\subsection{Interacting Network Components} 
Bridges, pluggable transports, and proxies are network components that 
circumvent censorship and interact with the Tor configuration interface. 
These components are shown in Fig.~\ref{fig:topology}.
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
		\caption{old flow} 
	\label{fig:old-flow}
\end{figure*}

@@

%We noticed four common challenges:  
%
%\begin{itemize}
%\item {\bfseries Challenge 1:} People are not qualified to answer the bridge and proxy questions asked or to choose between the transport choices given.  
%\item {\bfseries Challenge 2:} People feel compelled to configure a connection, even if they don't need one. 
%\item {\bfseries Challenge 3:} It was common for users to configure proxies, rather than trouble shooting bridges. 
%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next. The feedback did not guide users into specific actions.
%\end{itemize}

%These problems were illustrated by our participants:

%\begin{itemize}
%\item {\bfseries Proof of Challenge 1:} Of the five participants who could click directly to the network, three participants (P3,P4,P10) did not choose to connect directly.  Of the eleven participants who needed to configure their connection, eight (P1, P5, P6, P7, P8, P11, P13, P14, P16) chose to connect directly. One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection. Only one (P15) chose to configure when they needed to.
%\item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor. Three of the five (P3, P4, P10) configured a bridge for their connection. Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work. 
%\item {\bfseries Proof of Challenge 3:} All three of our participants who failed to circumvent the simulated censorship environment (P14, P15, P16) spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network. Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
%\item {\bfseries Proof of Challenge 4:} One participant (P14) tried the same configuration seven times, even though those settings failed each time. Another participant (P12) tries the same configuration three times, and only manages to connect through a technical artifact of the experiment even though that should not have worked. Both of these participants emphasized that they did not know what they should be doing. Other participants' interview responses also indicate a lack of feedback after failure cases (P8, P15, P16). 
%\end{itemize}

@@

\section{Redesigning the Configuration Interface}
\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
		\caption{new flow} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{bridge-screens.pdf} 
		\caption{bridge screens} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{proxy-screens.pdf} 
		\caption{proxy-screens} 
\end{figure*}

@@

%HEURISTICS
%\begin{enumerate}
%    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
%    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
%    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
%    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
%\end{enumerate}

@@

%EMPIRICALS
%\begin{enumerate}
%    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
%    \item {\bfseries  Time to Completion}: Time to completion. 
%    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
%\end{enumerate}

>>>>

\subsection{Interacting Network Components} 
\label{sec:components}
Bridges, pluggable transports, and proxies are network components that 
circumvent censorship and interact with the Tor configuration interface. 
These components are shown in Fig.~\ref{fig:topology}.
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

@@

@@

@@

\section{Redesigning the Configuration Interface}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf}
\hrule
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
\caption{
Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
We collapsed the two bridge screens into one;
similarly the two proxy screens.
We swapped the order of the bridge and proxy configuration
so it matches the order of network components (Section~\ref{sec:components}).
We added a summary screen as a last step before initiating a connection.\\
\textbf{F}: first screen;
\textbf{B/B1/B2}: bridge screens;
\textbf{P/P1/P2}: proxy screens;
\textbf{S}: summary screen;
\textbf{Pr}: progress bar.
}
\label{fig:flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{bridge screens} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{proxy-screens} 
\end{figure*}

@@

@@
